---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bepop

<!-- badges: start -->
[![R-CMD-check](https://github.com/sciensanogit/bepop/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sciensanogit/bepop/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of bepop is to make the population data from Belgium available in R.

## Installation

You can install the development version of bepop from [GitHub](https://github.com/) with:

```
# install.packages("devtools")
devtools::install_github("sciensanogit/bepop")
```

## Population datasets

the `bepop` package contains population files on different geographical levels (municipalities - districts - provinces -  regions - country). The datasets are names as follows:

* *BE_POP_MUNTY*: municipalities
* *BE_POP_ARRD*: districts
* *BE_POP_PROV*: provinces (+ Brussels Capital Region for simplicity)
* *BE_POP_RGN*: regions
* *BE_POP*: country

for more information on the content of each dataset, you can always consult the help-file by `?BE_POP`. The population structure of Belgium over the years was as follows:

```{r, echo = FALSE}
data("BE_POP")
betab <- aggregate(
  data = subset(BE_POP, subset = SEX == "MF" & AGE == "ALL"),
  POPULATION ~ YEAR,
  FUN = sum)

kableExtra::kable(betab)
```



## Data sources

The idea for this package is inspired by the [BelgiumMaps.StatBel package](https://github.com/bnosac/BelgiumMaps.StatBel), developed by Jan Wijffels at [BNOSAC](http://www.bnosac.be/index.php/blog/55-belgiummaps-statbel-r-package-with-administrative-boundaries-of-belgium).

The population files are obtained from the Statbel open data:

* **https://statbel.fgov.be/en/themes/population** includes information on the population of Belgium on the 1st of January for each year.

To calculate the mid-year population of year `x`, one should average the population of year `x` and year `x+1` 
